---
title: "6.2 移动平均"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
library(fpp2)
library(forecast)
library(extrafont)

# 导入中文字体
font_import(pattern = "simhei.ttf")  # simhei.ttf是中文字体的文件名，需要将其放在R工作目录下

# 加载字体
loadfonts(device = "win")

# 设置字体
Sys.setenv("font.family"="SimHei")
```

Type any R code in the chunk, for example:
```{r}
autoplot(elecsales) + xlab("年份") + ylab("亿瓦时") +
  ggtitle("年度电力销售量: 南澳大利亚")+
  theme(text = element_text(family = "SimHei"))+
  theme(plot.title = element_text(hjust = 0.5))
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
